Deterministic and statistical truncated KdV models for anomalous waves induced by abrupt depth change

### 2018-09-27 LatexNotes/Notes.tex
NM

\subsubsection{Final formulation}
Equation \eqref{varKdVugly} is essentially in the form we want to use, except that the notation is bad. In particular, we will want to reserve the symbol $H$ for the Hamiltonian. So making superficial changes to the notation gives
\begin{align}
2 \beta u_s + 3 \eps D^{-7/4} \, u u_x
+ \frac{4 \pi^2 \delta^2}{3 M^2} D^{1/2} \, u_{xxx} = 0
\end{align}
Importantly, $u(x,s)$ is $2\pi$-periodic in $x$ and has normalized energy $\mean{u^2} = 1$.
The definitions of each of the dimensionless variables in terms of the original, physical ones (denoted with a bar) are
\begin{align}
& u = D^{1/4} \, \bar{\eta}/a \\
& x = 2\pi \lambda_c^{-1} (\bar{x} - c \bar{t})  \\
& s = 2 \pi \beta M^{-1} \lambda_0^{-1} \bar{x}
\end{align}
A list of the fixed parameters is
\begin{align}
& \lambda_0 = \sqrt{g h_0}/f_p \quad \text{(upstream wavelength)} \\
& \eps = a / h_0 \quad \text{(dimensionless ratio of wave amplitude to depth)} \\
& \delta = h_0 / \lambda_0 \quad \text{(dimensionless ratio of depth to upstream wavelength)} \\
& \beta	\quad \text{(an unspecified small parameter, usually $\eps$ or $\delta^2$)}
\end{align}
Here is a list of the parameters that vary in space due to the fact that depth $d$ varies in space
\begin{align}
&\lambda_c = M \lambda_p = M \sqrt{gd}/f_p \quad \text{(characteristic wavelength as it varies in space)} \\
&D = d/h_0 \quad \text{(dimensionless depth ratio as it varies in space)} \\	
\end{align}

\vsp{10}

\subsubsection{Miscellaneous }

\subsubsection{My reformulation}

We therefore introduce dimensionless variables, denoted by a tilde
\begin{align}
& x = \frac{\lambda_p}{2\pi} \tilde{x} , \quad 
t = \frac{\lambda_p}{2\pi c} \tilde{t} , \quad
\eta = a \tilde{\eta} \\
& \xi = x-ct = \frac{\lambda_p}{2\pi} (\tilde{x} - \tilde{t}) = \frac{\lambda_p}{2\pi} \tilde{\xi}
\end{align}
Then in dimensionless variables (after dropping the tildes), the system is given by
\begin{equation}
\eta_t + \frac{3}{2}\eps \eta \eta_{\xi} + \frac{2 \pi^2}{3} \delta^2 \eta_{\xi \xi \xi} = 0
\end{equation}
where we have the dimensionless variables
\begin{align}
\eps = a/h_0 , \quad \delta = h_0/\lambda_p
\end{align}
In these dimensionless variables, we have that $\eta$ is periodic for $x \in [0, 2\pi)$ and we have $\mean{\eta^2} = 1$, just as intended.
Note, in the experiments, $\delta = 0.33$ and $\eps$ lies in the range $2.4 \times 10^{-3}$--$2.4 \times 10^{-2}$.

We will eventually want to rescale $t$, to look at long-time scales as is typically done in KdV analysis. Accordingly, we will define
\begin{equation}
\tau = \beta t
\end{equation}
where $\beta$ is usually either $\eps$ or $\delta^2$ (or we can choose it to be something more appropriate for the experiments). Of course, the effect of this rescaling would be to introduce a factor of $\beta$ in front of the first term $\eta_{\tau}$.

>>>>

\subsubsection{Final formulation}
Equation \eqref{varKdVugly} is essentially in the form we want to use, except that the notation is bad. In particular, we will want to reserve the symbol $H$ for the Hamiltonian. So making superficial changes to the notation gives
\begin{align}
2 \beta u_s + 3 \eps D^{-7/4} \, u u_x
+ \frac{4 \pi^2 \delta^2}{3 M^2} D^{1/2} \, u_{xxx} = 0
\end{align}
Importantly, $u(x,s)$ is $2\pi$-periodic in $x$ and has normalized energy $\mean{u^2} = 1$.
The definitions of each of the dimensionless variables in terms of the original, physical ones (denoted with a bar) are
\begin{align}
& u = D^{1/4} \, \bar{\eta}/a \\
& x = 2\pi \lambda_c^{-1} (\bar{x} - c \bar{t})  \\
& s = 2 \pi \beta M^{-1} \lambda_0^{-1} \bar{x}
\end{align}
A list of the fixed parameters is
\begin{align}
& \lambda_0 = \sqrt{g h_0}/f_p \quad \text{(upstream wavelength)} \\
& \eps = a / h_0 \quad \text{(dimensionless ratio of wave amplitude to depth)} \\
& \delta = h_0 / \lambda_0 \quad \text{(dimensionless ratio of depth to upstream wavelength)} \\
& \beta	\quad \text{(an unspecified small parameter, usually $\eps$ or $\delta^2$)}
\end{align}
Here is a list of the parameters that vary in space due to the fact that depth $d$ varies in space
\begin{align}
&\lambda_c = M \lambda_p = M \sqrt{gd}/f_p \quad \text{(characteristic wavelength as it varies in space)} \\
&D = d/h_0 \quad \text{(dimensionless depth ratio as it varies in space)} \\	
\end{align}
Note, in the experiments, $\delta = 0.33$ and $\eps$ lies in the range $2.4 \times 10^{-3}$--$2.4 \times 10^{-2}$.
